preparation

### 2025-02-27 data/preparation.Rmd
Updated data preparation
updated data
data preparation updated

parent <- parent %>% 
  rename(Pfinished = Finished)

@@

```{r wrangling}
# merging datasets
youtube <- full_join(parent, child, by = "PID")

@@

```{r wrangling}
# CATEGORICAL: Dealing with Likert scales - child survey items

@@

# definitely need to calculate cronbach's alphas...
```

>>>>

parent <- parent %>% 
  rename(Pfinished = Finished) %>% 
  # ensuring that Ptime is numeric
  mutate(Ptime = as.numeric(Ptime))

@@

```{r wrangling a}
# merging datasets
youtube <- full_join(parent, child, by = "PID")

@@

```{r wrangling b}
# CATEGORICAL: Dealing with Likert scales - child survey items

@@

# definitely need to calculate cronbach's alphas...

# temporary intermediate dataset
write_csv(youtube, "youtube.csv")
```
